---
title: "session_3.1.5"
author: "L Pandori"
date: "7/8/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(readr)
library(tidyr)
library(ggplot2)

```

## Introduction

Data description: North Pole Environmental Bottle Chemistry data from April/May 2000-2014. Data sourced from CTD-O2 system to measure conductivity, temp, depth, DO and Niskin bottle samples for salinity, O2 isotopes, TA, and nutrients.\

### Read in data

Data source: <https://arcticdata.io/catalog/view/doi:10.18739/A25T3FZ8X>

```{r import data, warning = FALSE, message = FALSE}
# "../" tells computer to go back levels of org in files, use tab to see options

# working directory is where rmd is stored

bg_chem <- read_csv('../data/BGchem2008data.csv')

```

## Analysis

### Calculate summary stats

```{r}
nitrate <- mean(bg_chem$NO3)
nitrite <- mean(bg_chem$NO2)
ammonium <- mean(bg_chem$NH4)
phos <- mean(bg_chem$P)
```

Mean nitrate value is `r nitrate`.
Mean nitrite value is `r nitrite`.

### Calculate mean Redfield Ratio

```{r}
ratio <-(nitrate + nitrite + ammonium)/phos
```

The redfield ratio is approximately `r round(ratio)`. 

### Plot Redfield Ratio

```{r}
plot(bg_chem$P, bg_chem$NO2 + bg_chem$NO3 + bg_chem$NH4)
```
